\huge A Usability Evaluation of Tor Launcher

### 2017-03-15 pets2017-paper/pets2017-paper.tex
expanded introduction; finished addressing intro comments

\section{Introduction}
Tor~\cite{dingledine2004tor} is an anonymity network that routes Internet traffic through a series of relays 
to make it difficult to observe sources and destinations. Tor Browser~\cite{torbrowser} is a modified Firefox browser that routes traffic through Tor, thereby simplifying the process of configuring Tor to use existing browsers. Although Tor Browser was originally designed for anonymity, many now use Tor Browser to circumvent Internet censorship. Many countries block Tor relays specifically to prevent their citizens from circumventing censorship~\cite{winter2012great}. Tor Browser is bundled with a graphical configuration interface, Tor Launcher, which allows users to bypass censorship by configuring various bridges, proxies, and transport protocols prior to connecting to Tor. Of course, these configuration options are only effective if users understand how to correctly use them. Thus, we performed a usability study wherein we simulated various censorship environments in order to examine the effectiveness of Tor Launcher and how it could be improved.

Improving Tor launcher has the obvious benefit of helping censored users connect to Tor, but this also benefits other Tor users since an increase in the overall number of users increases the anonymity set~\cite{dingledine2006anonymity}). In this paper, we describe how we started our usability evaluation by inspecting the interface (Section~\ref{sec:inspection}) and observing participants interact with it (Section~\ref{sec:qualitative}). Based on the insights from our observations, we proposed several changes to the interface (Section~\ref{sec:design}) and measured how successfully and quickly users connect to Tor before and after changes (Section~\ref{sec:quantitative}). Finally, we provide recommendations based on what we learned (Section~\ref{sec:recommendations}), we address limitations of our evaluation (Section~\ref{sec:limitations}), and frame our study in the context of existing work (Section~\ref{sec:related}). We hope that our usability evaluation serves as an informative case study and provides guidance on further improving Tor Launcher, as well as other privacy-enhancing technologies.

>>>>

\section{Introduction}
Tor~\cite{dingledine2004tor} is an anonymity network that routes Internet traffic through a series of relays 
to make it difficult to observe sources and destinations. Tor Browser~\cite{torbrowser} is a modified Firefox browser that routes traffic through Tor, thereby simplifying the process of configuring Tor to use existing browsers. Although Tor Browser was originally designed for anonymity, many now use Tor Browser to circumvent Internet censorship. Many countries block Tor relays specifically to prevent their citizens from circumventing censorship~\cite{winter2012great}. Tor Browser is bundled with a graphical configuration interface, Tor Launcher, which allows users to bypass censorship by configuring various bridges, proxies, and transport protocols prior to connecting to Tor. Of course, these options are only effective if users understand how to use them. Thus, we performed a usability study to examine the effectiveness of Tor Launcher and how it could be improved.

Improving Tor launcher has the obvious benefit of helping censored users connect to Tor, but this also benefits other Tor users since an increase in the overall number of users increases the anonymity set~\cite{dingledine2006anonymity}). Tor does not collect user interaction data from its real users, so we believe that usability testing research is critical to help users in heavily censored regimes and increase user adoption. In this paper, we: \\

\begin{itemize}
\item{Perform a qualitative and quantitative usability evaluation of Tor Launcher 5.0.3  under simulated censorship environments to determine why and how much it is or is not usable.}
\item{Contribute design changes that statistically significantly improve users' likelihood of connecting to Tor and also statistically significantly reduces the amount of time users take to connect.} 
\item{Provide recommendations beyond design changes to improve Tor Launcher, such as leveraging user input (requires research) and building an automated connection scheme (requires Tor-infrastructure work).}
\end{itemize}

Specifically, we describe how we started our usability evaluation by inspecting the interface (Section~\ref{sec:inspection}) and observing participants interact with it (Section~\ref{sec:qualitative}). Based on the insights from our observations, we proposed several changes to the interface (Section~\ref{sec:design}) and measured how successfully and quickly users connect to Tor before and after changes (Section~\ref{sec:quantitative}). Finally, we provide recommendations based on what we learned (Section~\ref{sec:recommendations}), we address limitations of our evaluation (Section~\ref{sec:limitations}), and frame our study in the context of existing work (Section~\ref{sec:related}). We hope that our usability evaluation serves as an informative case study and provides guidance on further improving Tor Launcher, as well as other privacy-enhancing technologies.
